Scalar Feedback based Joint Time-Frequency Precoder Interpolation for MIMO-OFDM Systems

### 2020-04-30 paper/main.tex
minor image size fix
Minor changes

\setlength{\textfloatsep}{0.7\baselineskip plus 0.2\baselineskip minus 0.5\baselineskip}
\def\imwidth{0.7}
%package list
\IEEEoverridecommandlockouts
\let\labelindent\relax
% \usepackage{breqn}
\usepackage{enumitem}
\usepackage{fleqn}
\usepackage{cite}
\usepackage{graphicx}
\usepackage[varg]{newtxmath}
\graphicspath{ {images/} }
\usepackage{pdfpages}
\usepackage{wrapfig}
\usepackage{fancyhdr}
\usepackage{lastpage}
\usepackage{lettrine}
\usepackage{amsmath}
% \usepackage{titlesec}
\usepackage[colorinlistoftodos]{todonotes}
\usepackage{float}
\usepackage[font={footnotesize}]{caption}
\usepackage[numbers,sort,square,compress]{natbib}
\usepackage[para]{footmisc}
\usepackage{xcolor}
\setlength{\belowcaptionskip}{-12pt}
\newcommand{\highlight}[1]{%
  \colorbox{red!50}{$\displaystyle#1$}}

@@

\includegraphics[width=0.7\columnwidth]{images/new-adpm.pdf}

@@

  quantized. We see that the subcarrier indicated by
  red arrows has a precoder whose parameters are determined jointly
  using the neighbouring parameters, both in time and frequency.}

@@

% \vspace{-1\baselineskip}
\subsection{Joint Time Frequency Interpolation}
\label{interp}
After obtaining the $\beta$ values (using the single bit feedback) at
the transmitter, we can construct the precoder at subcarrier indices
$pk$ or $pk+q$, keeping with the same notation as the previous
section. 
% To construct precoders for the rest of the subcarriers, we will use
% precoder parameters from both the ``past'' and ``future'' time
% instances to do the interpolation (using backtracking to ensure
% causality). When using future time instances, the implication is that the precoder
% estimation is improved at a later time instant i.e. after receiving
% the feedback of the next set of subcarriers. Note that the precoder
% used for transmission is causally obtained, while the ``future''
% correction of past precoders merely improves the interpolation
% accuracy. 
In Fig.~\ref{fig:adpm-fig}, each parameter is interpolated
using the neighbouring subcarriers using bilinear interpolation
(equivalent to linear interpolation in two dimensions). These
interpolated values are then used to reconstruct the precoding
matrices all together by applying the reverse transformation of
breaking the precoder into independent parameters as given in
Equation~\ref{eq:decompose}. Inorder to improve the precoder estimates 
and interpolation accuracy we walkback to improve the past estimates by interpolating
upon the current estimates. Thus, the approach here is able to exploit the time and frequency correlation jointly to enhance performance.
% To construct the precoders for the rest of the subcarriers, we will
% use the  parameters from the previously determined subcarriers.
%

>>>>

\setlength{\textfloatsep}{0.7\baselineskip plus 0.2\baselineskip minus 0.5\baselineskip}
\def\imwidth{0.62}
%package list
\IEEEoverridecommandlockouts
\let\labelindent\relax
% \usepackage{breqn}
\usepackage{enumitem}
\usepackage{fleqn}
\usepackage{cite}
\usepackage{graphicx}
\usepackage[varg]{newtxmath}
\graphicspath{ {images/} }
\usepackage{pdfpages}
\usepackage{wrapfig}
\usepackage{fancyhdr}
\usepackage{lastpage}
\usepackage{lettrine}
\usepackage{amsmath}
% \usepackage{titlesec}
\usepackage[colorinlistoftodos]{todonotes}
\usepackage{float}
\usepackage[font={footnotesize}]{caption}
\usepackage[numbers,sort,square,compress]{natbib}
\usepackage[para]{footmisc}
\usepackage{xcolor}
\setlength{\belowcaptionskip}{-12pt}
\newcommand{\highlight}[1]{%
  \colorbox{red!50}{$\displaystyle#1$}}

@@

\includegraphics[width=0.68\columnwidth]{images/new-adpm1.pdf}

@@

  quantized. Subcarriers indicated by red arrows have precoders whose
  parameters are determined using the neighbouring parameters, both in
  time and frequency. The black arrow indicates refinement of past
  estimates.}

@@

% \vspace{-1\baselineskip}
\subsection{Joint Time Frequency Interpolation}
\label{interp}
After obtaining the $\beta$ values (using the single bit feedback) at
the transmitter, we can construct the precoder at subcarrier indices
$pk$ or $pk+q$, keeping with the same notation as the previous
section. 
% To construct precoders for the rest of the subcarriers, we will use
% precoder parameters from both the ``past'' and ``future'' time
% instances to do the interpolation (using backtracking to ensure
% causality). When using future time instances, the implication is that the precoder
% estimation is improved at a later time instant i.e. after receiving
% the feedback of the next set of subcarriers. Note that the precoder
% used for transmission is causally obtained, while the ``future''
% correction of past precoders merely improves the interpolation
% accuracy.

In Fig.~\ref{fig:adpm-fig}, each parameter is interpolated using the
neighbouring subcarriers using bilinear interpolation (equivalent to
linear interpolation in two dimensions). These interpolated values are
then used to reconstruct the precoding matrices all together by
applying the reverse transformation of breaking the precoder into
independent parameters as given in
Equation~\ref{eq:decompose}. Precoder estimates are calculated using
the current and past data, though the earlier precoder estimates
arexsa improved by refining the past past estimates through
interpolation with current estimates (indicated by the black arrow in
Fig.~\ref{fig:adpm-fig}). Thus, the approach here is able to exploit
the time and frequency correlation jointly to enhance performance.

% To construct the precoders for the rest of the subcarriers, we will
% use the  parameters from the previously determined subcarriers.
%
